\texttt{vqtl}: An \texttt{R} package for Mean-Variance QTL Mapping

### 2018-07-11 Package_vqt_Manuscript.tex
edits

Traditional quantitative trait locus (QTL) analyses have focused on discovering ``mean QTL'', regions of the genome where allelic variation drives heterogeneity of phenotype mean, while assuming that the residual variance, that is, the intrinsic stability or noisiness of the phenotype, is identical for every individual in the mapping population.
Recent work, however, has challenged the assumption of homogeneous residual variance and sought to identify an additional type of QTL---those that influence the extent of residual variance, sometimes termed ``variance QTL'' (vQTL) \citep{Pare2010,Ronnegard2011a,Ronnegard2012,Cao2014}.

>>>>

Traditional quantitative trait locus (QTL) analyses have focused on discovering ``mean QTL'', regions of the genome where allelic variation drives heterogeneity of phenotype mean, while assuming that the residual variance, that is, the intrinsic stability or noisiness of the phenotype, is identical for every individual in the mapping population.
However, it has long been recognized that the extent of residual variation is itself a heritable trait \citep{Falconer1965,Lynch1998}.
This phenomenon has been described theoretically \citep{Hill2004-uo,Hill2010} and demonstrated in inbred model organisms \citep{Sorensen2015,Ayroles2015} and crops \citep{Yang2012-aw,Forsberg2015} and exploited in livestock improvement efforts \citep{Mulder2008,Ibanez-Escriche2008-ie}.
Recent work, has begun to recognize heterogeneous residual variance in mapping efforts by identifying an additional type of QTL---those that influence the extent of residual variance, sometimes termed ``variance QTL'' (vQTL) \citep{Pare2010,Ronnegard2011a,Ronnegard2012,Cao2014}.
